\documentclass[twocolumn]{article}
\usepackage[margin=25mm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\newcommand{\HorRule}{\color{Black}\rule{\linewidth}{2pt}}
\providecommand{\keywords}[1]
{
  \textbf{\textit{Keywords---}} #1
}

\title{Joint Optimization of Trajectory Planning and Task Scheduling in
Heterogeneous Multi-UAV System}
\author{Praneeth Reddy, IIT Ropar}
\date{}

\begin{document}

\maketitle
\begin{abstract}
    The use of unmanned aerial vehicles (UAV) as a new sensing paradigm is emerging for surveillance and tracking
applications, especially in the infrastructure-less environment. One such application of UAVs is in the construction industry where currently prevalent manual progress
tracking results in schedule delays and cost overruns. In
this paper, we develop a heterogeneous multi-UAV framework for progress tracking of large construction sites. The
proposed framework consists of Edge UAV which coordinates the data relay of the visual sensor-equipped Inspection UAVs (I UAV s) to the cloud. Our framework jointly
takes into consideration the trajectory optimization of the
Edge UAV and the stability of system queues. In particular, we develop a Distance and Access Latency Aware
Trajectory (DLAT) optimization that generates a fair access schedule for I UAV s. In addition, a Lyapunov based
online optimization ensures the system stability of the average queue backlogs for data offloading tasks. Through a
message based mechanism, the coordination between the
set of I UAV s and Edge UAV is ensured without any
dependence on any central entity or message broadcasts.
The performance of our proposed framework with joint
optimization algorithm is validated by extensive simulation results in different parameter settings.
\end{abstract}
\keywords{Path Planning Task Scheduling, Data Offloading, Construction Site Monitoring, Unmanned Aerial
Vehicles (UAVs), Lyapunov Optimization}
\section{Introduction}
The unmanned aerial vehicle (UAV) based solutions are
emerging in various domains such as wireless sensing \cite{mozaffari2019tutorial},
payload delivery \cite{ruggiero2018aerial}, precision agriculture \cite{boursianis2020internet}, help and
rescue operations \cite{waharte2010supporting}, etc. Moreover, with the current
trend of automation, sensing and information exchange in Industry 4.0, UAV based applications are also finding
their place in the construction industry especially for resource tracking and progress monitoring using aerial imagery. Such solutions are helpful in infrastructure-less
large construction sites as they provide ease of deployment, quick access to the ground-truth data and higher
reachability and coverage \cite{hamledari2018uav}. Further, the autonomous
or semi-autonomous UAV based solutions could facilitate
progress monitoring, building inspections (for cracks or
other defects), safety inspections (to find any environmental hazards) and many more construction-specific audits automatically. The UAV based visual monitoring of
under-construction projects also allows simultaneous observability of ground-truth data by different collaborating
entities. Availability of such data and information helps
in timely assessments that could reduce schedule delays,
cost overruns, resource wastage and financial losses which
are not uncommon in construction projects.
\\
\\
A plausible solution to address the aforementioned
challenges could be a Mobile Edge Computing (MEC)
\cite{mao2017survey} based heterogeneous multi-UAV framework. Such a
framework along with the prior geometric knowledge available about the construction site as gathered from a Building Information Model (BIM)\cite{golparvar2011integrated} could help create an effective multi-UAV based visual monitoring system for construction sites. As for any constrained environment, the
optimization of computational resources is central to develop a solution. The integration of UAVs and MEC into
a single framework could facilitate that with efficient data
collection/processing from the UAV based dynamic sensors in infrastructure-less environments \cite{nguyen2020towards}. In addition,
an MEC based framework can help to perform partial
computation offloading wherein a part of data is processed
by the UAVs while the rest gets offloaded to the cloud.
\\
\\
An MEC based UAV framework is not new and the deployment of the UAVs as base stations or edge servers
is widely studied \cite{wan2019towards} \cite{abbas2017mobile}. These studies reflect on the flexibility in deployment of UAV based edge computing
components. However, there is a problem of buffer overflow of UAVs due to the limited on-board processing and
the shared bandwidth to transfer data to the cloud which
leads to instability in the system. In addition, the dynamic nature of such systems with varying data traffic
and continuous movement of UAVs makes it difficult to
stabilize or control the system in a deterministic manner. Researchers have used online Lyapunov optimization
\cite{neely2010stochastic} to address such system instabilities. Lyapunov optimization considers the stability of the system with time
varying data and optimizes time averages of system utility
and queue backlogs
\\
\\
In this paper, we address the challenges of deploying
a heterogeneous multi-UAV system for construction site
monitoring by the joint optimization of UAV trajectory
planning and data offloading task scheduling. The proposed framework employs two types of UAVs viz. Inspection UAVs I UAV s and Mobile Edge UAVs (Edge UAV ).
While the former is deployed as visual sensors to collect
visual data from different locations of the site, the latter
interacts and collects data from I UAV s, and offloads the
same to the cloud. The core objective of the framework
is to minimize the total energy consumption of the system while considering the data queue backlogs of I UAV s
and Edge UAV and also jointly optimizing the trajectory
of the Edge UAV in accordance with the trajectories of
I UAV s having minimum access latency and travel distance. The online resource management such as transmission power and processor frequency of the Edge UAV is
evolved using Lyapunov optimization (as in \cite{zhang2018stochastic}).
The rest of the paper is organised as follows: Section
2 presents the proposed heterogeneous multi-UAV framework for construction site monitoring. The overall system
objective is discussed in Sections 3. Sections 4 and 5 discuss the trajectory optimization and Lyapunov based system stability, respectively. The simulation setup has been
presented in Section 6. Section 7 discusses the results
gathered from the experiments while Section 8 concludes
the paper.
\section{Heterogeneous Multi-UAV Framework}
Figure ?? depicts the overall multi-UAV framework with
all its components. The system consists of two heterogeneous UAVs i.e. a set of Inspection UAVs I UAV =
{I UAV1, I UAV2, I UAV3, ....., I UAVN } and a Mobile
Edge UAV (Edge UAV ). I UAV s are smaller in size and
are more agile. They collect visual data from a set of
Point of Interests (PoIs) denoted as L = {l1, l2, l3....lk}
across the construction site. As the construction sites are
infrastructure-less environments, there are limited Access
Points (AP) available for connectivity to the cloud. Further, the I UAV s possess limited connectivity range\citet
makes it difficult for them to transfer data to cloud directly. In addition, the I UAV s move in the 3D Cartesian
coordinate system. The Edge UAV , which is larger in size
and possesses higher computational capabilities, coordinates with the I UAV s to relay the data (after partially
processing the same) to the cloud. Edge UAV always
maintains a constant height and thus its trajectory lies in
an horizontal plane.
\\
\\
The communication between I UAV and Edge UAV
(A2A channel) has limited range and bandwidth. We
have assumed the achievable data transmission rate of
the I UAVi
in a given time slot as d
of f
i
(t). Further, The
height of the Edge UAV is h which is dependent on coverage range r and line of sight (LoS) loss caused due to
environmental effects \cite{al2014optimal}.
\\
\\
The A2A channel power gain ($\zeta$) from I UAV to
Edge UAV can be given as:
\\
\big$\zeta$ = g_0 * (dis_0/dis_t)^$\theta$
\\
where $g_0$ is the path loss constant, $dis_0$ is the reference
distance, $dis_t$ distance between the UAV_s, 
and $\theta$ is the
path loss exponent.
\subsection{Data collection and offloading}
Each PoI (l_i) is a tuple (< d_i
, $\psi_i$ $>$) where di specifies the
amount of data (images) to be collected and ψi denotes the
coordinates of the site locations in 3D space. The sequence
of PoIs to be visited is provided to I UAV s and same is
also shared with the Edge UAV . During the traversal
along the sequence of PoIs, the limited buffer may make
the I UAV wait at some PoIs along the trajectory until
it offloads the data to the Edge UAV .


\bibliography{PraneethReddyNalla_2023AIM1010}
\bibliographystyle{alpha}

\end{document}
